Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-13 paper/paper.tex
Notation and prop4 fixes.

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}

@@

\section{Some Maths}
A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
$i: P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $i: P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
 vertices.

@@

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
$i_{k}: P \rightarrowtail T$ and $i_{k}: P \hookrightarrow T$ respectively.

@@

\begin{proposition}
    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $i_{k}(p) = t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

\begin{proposition}
    More powerfully, if $i_{k}(p) = t$ then $\operatorname{nds}(p)[k, k+1, \ldots] \preceq
    \operatorname{nds}(t)$.
\end{proposition}

@@

\begin{proposition}
    If $i_{k}(p) = t$ and $i_{k}(q) = u$ then $\operatorname{paths}(p, q, 2) \le
    \operatorname{paths}(t, u, 2) + k$.
\end{proposition}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$, and
    and $p,q\in\operatorname{V}(G)$, with $p$ and $q$ adjacent if there are at least $n$
    simple paths of length exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$
    isomorphism $i_{k}: P \rightarrowtail T$ induces a new subgraph-except-$k$ isomorphism
    $i^{n, 2}_{k} : P^{n, 2}\rightarrowtail T^{n - k, 2}$.
\end{proposition}

>>>>

\usepackage{ijcai16}
\usepackage{times}
\usepackage{complexity}
\usepackage{microtype}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{cleveref}
\usepackage{tikz}
\usepackage{mathtools}

@@

\section{Some Maths}
A non-induced subgraph isomorphism from a graph $P$ to a graph $T$ is an injective mapping
$P \rightarrowtail T $ which maps adjacent vertices to adjacent vertices. An induced subgraph
isomorphism $P \hookrightarrow T$, additionally maps non-adjacent vertices to non-adjacent
 vertices.

@@

We define a subgraph-except-$k$ isomorphism from $P$ to $T$ to be a subgraph isomorphism from all
but $k$ vertices of $P$ to $T$; this may be non-induced or induced, written
$P \prescript{}{k}{\rightarrowtail} T$ and $P \prescript{}{k}{\hookrightarrow} T$ respectively.

@@

\begin{proposition}
    Let $p$ be a vertex of $P$ and $t$ a vertex in $T$. For both non-induced and induced
    subgraph-except-$k$ isomorphisms, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{deg}(p) \le \operatorname{deg}(t) + k$.
\end{proposition}

\begin{proposition}
    More powerfully, if $p \prescript{}{k}{\mapsto} t$ then
    $\operatorname{nds}(p)[k+1, k+2, \ldots] \preceq \operatorname{nds}(t)$.
\end{proposition}

@@

\begin{proposition}
    If $p \prescript{}{k}{\mapsto} t$ and $q \prescript{}{k}{\mapsto} u$ then
     $\operatorname{paths}(p, q, 2) \le \operatorname{paths}(t, u, 2) + k$.
\end{proposition}

@@

\begin{proposition}
    For a graph $G$, let $G^{n, \ell}$ be the graph with vertex set $\operatorname{V}(G)$. Let $p$ and $q$ be adjacent vertices of $G^{n, \ell}$, if there are at least $n$ simple paths of length
    exactly $\ell$ between $p$ and $q$ in $G$. Then any subgraph-except-$k$ isomorphism
    $P \prescript{}{k}{\rightarrowtail} T$ induces a new subgraph-except-$k$ isomorphism
    $P{n, 2}\prescript{}{k}{\rightarrowtail} T^{n - k, 2}$.
\end{proposition}
